\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{marginnote}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{array}

\begin{document}

\pagestyle{empty}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\noindent
\begin{tabularx}{\linewidth}{@{}lR@{}}
\multirow{2}{*}{\noindent\textbf{\Large{Shawn Patrick Rigdon}}} & \footnotesize{828-550-3668} \\[-4pt]
& \footnotesize{shawn.patrick.rigdon@gmail.com} \\[-4pt]
\end{tabularx}

\smallskip
\noindent\rule[\baselineskip]{\linewidth}{1.5pt}


\medskip
\noindent\textbf{\large{Research Interests}}

\medskip
\noindent\footnotesize{Signal processing, machine learning and computational neuroscience;
computer vision, specifically object detection and tracking;
data fusion for object/event classification.
}

\bigskip
\noindent\textbf{\large{Education}}

\medskip\noindent
\begin{tabular}{@{}ll@{}}
\footnotesize{The Georgia Institute of Technology:} & \footnotesize{MS in Electrical and Computer Engineering}\\[5pt]
\footnotesize{Western Carolina University:} & \footnotesize{BS in Electrical Engineering}\\
\footnotesize{(\textit{magna cum laude})} & \footnotesize{BS in Applied Mathematics}\\
\end{tabular}
\marginnote{\footnotesize{\textit{2014}}}[-12pt]
\marginnote{\footnotesize{\textit{2009}}}[8pt]

\bigskip
\noindent\textbf{\large{Teaching Experience}}

\medskip\noindent
\begin{tabular}{@{}ll@{}}
\footnotesize{The Georgia Institute of Technology} & \footnotesize{Circuit Analysis (ECE2040)}\\
\footnotesize{\textit{Teaching Assistant}} & \footnotesize{TESSAL (Teaching Enhancement via Small Scale Affordable Labs) Center}\\
& \footnotesize{Fundamentals of Digital System Design
(ECE2020)}\\
\end{tabular}
%\bigskip
%\noindent\textbf{\Large{Teaching Experience} -- The Georgia Institute of Technology}

\bigskip
\noindent\textbf{\large{Professional Experience}}

\newcommand{\lwidth}{\hsize=.47\hsize\linewidth=\hsize}
\newcommand{\rwidth}{\hsize=1.53\hsize\linewidth=\hsize}

\medskip\noindent
%\begin{tabularx}{\textwidth}{@{}lR@{}}
\begin{tabularx}{\textwidth}{@{} >{\lwidth}L >{\rwidth}R}
\footnotesize{Computational Modeling and Software Services, LLC} &
\multirow[t]{2}{\linewidth}{\footnotesize{\noindent
Help small and startup tech businesses implement solutions to complex computational problems requiring
automated decision making from real time data streams.  Assistance on the full pipeline of real time
system software design including hardware interfacing, data acquisition and processing, machine learning
techniques, and system deployment at scale.
}}\\
\footnotesize{\textit{Owner}} & \\
\end{tabularx}
\marginnote{\footnotesize{\textit{2020}}}[-20pt]

\smallskip\noindent
%\begin{tabularx}{\textwidth}{@{}lX@{}}
\begin{tabularx}{\textwidth}{@{} >{\lwidth}L >{\rwidth}R}
\footnotesize{FLIR Systems, Inc.} &
\multirow[t]{2}{\linewidth}{\footnotesize{\noindent
Firmware/software development for embedded stereo cameras
for people tracking in a retail environment. Application areas include: image processing, traffic counting,
employee/customer classification using vision and inertial sensor data fusion, BLE beacon advertising.
Designed automated mfg. processes (e.g. HW functionality testing, focusing and calibration of stereo
lenses) to optimize product scalability.
}}\\
\footnotesize{\textit{Software Engineer}} & \\
\end{tabularx}
\marginnote{\footnotesize{\textit{2015-2020}}}[-20pt]

\bigskip\bigskip\noindent
%\begin{tabularx}{\textwidth}{@{}lX@{}}
\begin{tabularx}{\textwidth}{@{} >{\lwidth}L >{\rwidth}R}
\footnotesize{Liberty Defense Technologies, Inc.} &
\multirow[t]{2}{\linewidth}{\footnotesize{\noindent
Lead software architect of real time microwave imaging system for concealed weapon detection. The position
was mainly responsible for reconstructing and processing images from data given by a short range mm wave radar
transceiver. This required integration of several hardware components including a stereo camera used to locate
subjects in the scene.  To achieve a real time frame rate, many of the algorithms were written using CUDA to
parallelize on an onboard Nvidia GPU.  Other responsibilities included implementing fast algorithms for
person/object segmentation, triggering captures and other timing between camera and microwave images, and
generating training data for object detection models.
}}\\
\footnotesize{\textit{Sr. Software Engineer}} & \\
\end{tabularx}
\marginnote{\footnotesize{\textit{2019}}}[-20pt]

\bigskip\bigskip\bigskip\medskip\noindent
%\begin{tabularx}{\textwidth}{@{}lX@{}}
\begin{tabularx}{\textwidth}{@{} >{\lwidth}L >{\rwidth}R}
\footnotesize{TekTone Sound and Signal Mfg., Inc.} &
\multirow[t]{2}{\linewidth}{\footnotesize{\noindent
Designed embedded hardware for nurse call products deployed in
hospitals and assisted living facilities.  Designed the first UL listed wireless nurse call system.
}}\\
\footnotesize{\textit{Hardware Engineer}} & \\
\end{tabularx}
\marginnote{\footnotesize{\textit{2010-2013}}}[-19pt]

\vspace{-5pt}\noindent
%\begin{tabularx}{\textwidth}{@{}lX@{}}
\begin{tabularx}{\textwidth}{@{} >{\lwidth}L >{\rwidth}R}
\footnotesize{Space and Naval Warfare Systems Command} &
\multirow[t]{2}{\linewidth}{\footnotesize{\noindent
Project manager overseeing contracted air traffic control systems installations.
}}\\
\footnotesize{\textit{Project Engineer}} & \\
\end{tabularx}
\marginnote{\footnotesize{\textit{2010}}}[-19pt]

\vspace{-5pt}\noindent
%\begin{tabularx}{\textwidth}{@{}lX@{}}
\begin{tabularx}{\textwidth}{@{} >{\lwidth}L >{\rwidth}R}
\footnotesize{Haywood Electric Membership Corporation} &
\multirow[t]{2}{\linewidth}{\footnotesize{\noindent
Substation installation and debugging of TWACS, an automated meter reading system.
Led company wide adoption of North Carolina One Call System (an online database application for
locating underground wire).
}}\\
\footnotesize{\textit{Systems Engineer Intern}} & \\
\end{tabularx}
\marginnote{\footnotesize{\textit{2008-2010}}}[-19pt]

\bigskip
\noindent\textbf{\large{Publications}}\vspace{5.3pt}\\
\noindent
\footnotesize{M. Woldeyohannes, J. Schenk, R. Ingel, S. Rigdon, M. Pate, J. Graham, M. Clare, W. Yang, M. Fiddy, ``Internal Field Distribution Measurement in 1-D Strongly Anisotropic Sub-Wavelength Periodic Structures of Finite Length,'' Optics Express Vol. 19, Issue 1 (Jan. 3, 2011) pp: 81-92.}

\bigskip
\noindent\textbf{\large{Presentations}}\vspace{5.3pt}\\
\footnotesize{``Enormous  Field  Enhancement  in  Periodic  Birefringent Media,''
National Conference of Undergraduate Research, University of Wisconsin, LaCrosse}\marginnote{\footnotesize{\textit{2009}}}[-10pt]

\medskip\noindent
\footnotesize{``Analysis of Force Controlled Arm Movement,'' Undergraduate Expo, Western Carolina University}
\marginnote{\footnotesize{\textit{2009}}}

\bigskip
\noindent\textbf{\large{Honors and Awards}}\vspace{5.3pt}\\
\noindent\footnotesize{President's Fellowship Recipient, The Georgia Institute of Technology}
\marginnote{\footnotesize{\textit{2013}}}

\medskip
\noindent\footnotesize{Most Outstanding Senior in Electrical Engineering, Western Carolina University}
\marginnote{\footnotesize{\textit{2009}}}

\medskip
\noindent\footnotesize{Freshman Math Award, Western Carolina University}
\marginnote{\footnotesize{\textit{2005}}}

\bigskip
\noindent\textbf{\large{Software Tools}}

\medskip\noindent
\begin{tabular}{@{}lp{11cm}@{}}
\footnotesize{Languages:} & \footnotesize{C, C\texttt{++}, Python, Lua, some exposure to C\raisebox{2pt}{\texttt{\#}}, Perl, MySQL}\vspace{0.5mm}\\
\footnotesize{Tools and Utilities:} & \footnotesize{MATLAB, GNU Octave, Git, Visual Studio, Eclipse, Code::Blocks, Qt, OpenCV,}\\
                                    & \footnotesize{Caffe, Torch, TensorFlow, CUDA, \LaTeX, Maple, Mathematica, PADS PCB Layout,}\\
                                    & \footnotesize{OrCAD Schematic Capture}\vspace{0.5mm}\\
\footnotesize{Operating Systems:}   & \footnotesize{Microsoft Windows, Linux}\\
\end{tabular}


\end{document}
